In Depth Analysis of Event Patterns in Crisis Situations

### 2024-01-22 outputs/paper/paper.qmd
- Edited the README page to make it look more professional - Added the Abstract on the paper.

---
title: "In Depth Analysis of Event Patterns in Crisis Situations"
subtitle: "City of Toronto Data"
author: 
  - Vanshika Vanshika
thanks: "Code and data are available at: https://github.com/vanshikav2/Data_Analysis_1."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "In Depth Analysis of Event Patterns in Crisis Situations"
subtitle: "City of Toronto Data"
author: 
  - Vanshika Vanshika
thanks: "Code and data are available at: https://github.com/vanshikav2/Data_Analysis_1."
date: today
date-format: long
abstract: "Toronto Police Services' 10-year-long dataset on Persons in Crisis Calls for Service Attended was used to conduct an in-depth analysis of the major PIC call event: Suicide and its data characteristics. It is found that there is a direct relation/trend that can be observed between suicide PIC calls and several factors such as the specific time of the day, day of the week, and identifed hotspot geographical location. This is important as it's essential to analyze the patterns of suicide PIC calls to effectively deal with the problem at its root."
format: pdf
number-sections: true
bibliography: references.bib
---
